%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {FullStack Developer} % Job title
    {PT. Alfaeeza Niaga Internasional} % Organization
    {Indonesia} % Location
    {Mar. 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Building a library management web application with ReactJs as frontend and Dotnet as backend.}
        \\
        \item {Researching and determining the best technologies for the application}
        \\
        \item {Writing functional code using typescript and react js. Building backend to serve data using GraphQL API.}
        \\
        \item {Testing the application rigorously, identifying issues and debugging}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {FrontEnd Developer} % Job title
    {PT. Hanatek(Freelance)} % Organization
    {Indonesia} % Location
    {Apr 2022 - Aug 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item { Building and planning an organization portal website to support organization online activities, such as news, article publishing, job vacancies information, etc. }
        \\
        \item { Building administrator website to organize the content of the website. Providing front-end support in a small team of four. }
        \\
        \item{ Researching and determining the best technologies for the application}
        \\
        \item{ Writing functional code using typescript and react js}
        \\
        \item{ Testing the application rigorously, identifying issues and debugging }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {FrontEnd Developer} % Job title
    {PT. Minda Perdana Indonesia} % Organization
    {Indonesia} % Location
    {Mar. 2021 - Mar. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item { Building and improving an E-learning platform to support customer’s education activities. }
        \\
        \item { Creating features such as Calendar based course scheduling, implementing SCORM features, online surveys and online test activities.}
        \\
        \item { Other tools implemented includes instructor management, schedule and course management and student management. }
        \\
        \item { Writing functional code using javascript and reactjs }
        \\
        \item { Testing the application rigorously, identifying and debugging }
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
